\OurTool{}: Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles\\[1em] Supplementary material

### 2019-06-21 IPANEMAP-2019.tex
Updates from Overleaf

\subsection*{The \OurTool{} method}
\bsi{Ce chapitre est vraiment très réussi, il explique vraiment bien ce qu'on fait et c'est accessible meme pour des polios de biologistes. je trouve dommage qu'il soit cantoné au Mat et Met. A mon avis il faudrait soit le mettre tel quel comme premier chapitre des résultats, soit en faire une version light sans les détails de calculs le mettre comme premier chapitre des résultats et ne laisser que les calculs dans le Mat et Met}  
\ypi{Dans la mesure où l'intro est courte, et étant donné le titre, je ne pense pas que sa présence en Mat Met limite  sur visibilité. En plus, c'est typiquement là où tu le trouves d'habitude dans ce type de papier (cf Rsample).}
We introduce the Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles (\OurTool{}), a novel approach that integrates the signal produced by various chemical probes. It performs clustering based on multiple sets of structures sampled in different experimental conditions, to ultimately return a set of structures that are representative of the dominant clusters. Its underlying rationale is that the prominent presence of a stable secondary structure within the  (pseudo-)Boltzmann ensembles induced by multiple experimental conditions should increase its likelihood to be (one of) the native structure(s) for a given RNA. It is thus hoped that integrating several reactivity profiles may be used to promote the native structure as one of the dominant structures within the multi-ensemble, and help circumvent the limitation of pseudo-energies derived from single reactivity profile, which are generally not sufficient to elect the native structure as its minimum (pseudo)-free energy candidate. In other words, combining ensembles of structures generated using multiple probing experiments is likely to denoise the Boltzmann (multi-)ensemble, and thus mitigate systematic biases induced by experimental conditions and reagents.

@@

Our method, summarized in Figure~\ref{fig:approach}, takes as input a set $\mathcal{D}$ of probing experiments, each materialized by a reactivity profile. It starts by producing sets of representatives structures for each of the reactivity profiles using a SHAPE-directed variant of the classic Ding-Lawrence algorithm~\citep{Ding2003}. Following Deigan\etal\cite{Deigan2009}, soft constraints are used to complement the free energy contributions of the classic Turner energy model with pseudo energy contributions resulting from reactivity profiles derived from SHAPE probing experiments.  Given a reactivity $R_i$ for a position $i$, we associate a free-energy bonus to unpaired positions, defined as
$$\Delta G(i) = m \log(R_i +1 )+b$$ 
using $m=1.3$ and  $b=-0.4$. Those values are compared to those used by Deigan\etal\cite{Deigan2009}, based on the rationale that lower absolute values for pseudo-energy bonuses increase the chance of structures being simultaneously supported by multiple conditions. Those pseudo energy contributions effectively direct our predictions towards a subset of structures that are in good agreement with probing data.

@@

\newcommand{\Bull}[1]{{\sffamily #1}~\raisebox{1pt}{\tikzcircle[black, fill=cluster#1]{3pt}}}

\newcommand{\BullLab}[1]{Cluster \Bull{#1}}

\colorlet{clusterA}{SeaGreen}
\colorlet{clusterB}{Yellow}
\colorlet{clusterC}{gray}
\definecolor{clusterD}{HTML}{AFAFE9}
\colorlet{clusterE}{OliveGreen}
\colorlet{clusterF}{blue!90!black}
\colorlet{clusterG}{Orange}
\colorlet{clusterH}{SeaGreen!40}

@@

\paragraph{Comparison and clustering of conditions.}
Faced with diverse probing conditions, we first assess the compatibility of the conclusions drawn from different probing data, including the probing-free run of \OurTool as a control. We use the methodology described in the material and methods ~\ref{sec:dotplots} and, for each condition, compute the base pair probability distribution (a.k.a. dot-plot) in the  pseudo-Boltzmann ensemble, induced by the reactivity profile. We then computed the ensemble distance, the squared Euclidean distance between dot plots, for each pair of conditions. Figure~\ref{fig:PCA} summarizes the pairwise distance, projected onto a 2D surface by a principal component analysis.

@@

@@

	\caption{Discretized ensemble distance induced by conditions. Conditions ordered by spectral biclustering. Conditions regrouped within clusters by k-mean clustering appear as blocks on the x and y axis.\bsi{pourquoi les clusters E et F ne sont ils pas regroupés comme les autres?}}\label{fig:biclustering}
\end{figure}

>>>>

\subsection*{The \OurTool{} method}
\bsi{Ce chapitre est vraiment très réussi, il explique vraiment bien ce qu'on fait et c'est accessible meme pour des polios de biologistes. je trouve dommage qu'il soit cantoné au Mat et Met. A mon avis il faudrait soit le mettre tel quel comme premier chapitre des résultats, soit en faire une version light sans les détails de calculs le mettre comme premier chapitre des résultats et ne laisser que les calculs dans le Mat et Met}  
\ypi{Dans la mesure où l'intro est courte, et étant donné le titre, je ne pense pas que sa présence en Mat Met limite  sur visibilité. En plus, c'est typiquement là où tu le trouves d'habitude dans ce type de papier (cf Rsample).} \bsi{OK je propose la chose suivante:on laisse tt comme ca le math et met, mais on commence les résultats par un mini-chapitre du genre "principles of IPANEMAP" IPANEMAP relies on .. prediction with RNAsubopt ... sampling ... clustering .. evaluation by front pareto.. Its originality relies on ... See material and methods for details }
We introduce the Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles (\OurTool{}), a novel approach that integrates the signal produced by various chemical probes. It performs clustering based on multiple sets of structures sampled in different experimental conditions, to ultimately return a set of structures that are representative of the dominant clusters. Its underlying rationale is that the prominent presence of a stable secondary structure within the  (pseudo-)Boltzmann ensembles induced by multiple experimental conditions should increase its likelihood to be (one of) the native structure(s) for a given RNA. It is thus hoped that integrating several reactivity profiles may be used to promote the native structure as one of the dominant structures within the multi-ensemble, and help circumvent the limitation of pseudo-energies derived from single reactivity profile, which are generally not sufficient to elect the native structure as its minimum (pseudo)-free energy candidate. In other words, combining ensembles of structures generated using multiple probing experiments is likely to denoise the Boltzmann (multi-)ensemble, and thus mitigate systematic biases induced by experimental conditions and reagents.

@@

Our method, summarized in Figure~\ref{fig:approach}, takes as input a set $\mathcal{D}$ of probing experiments, each materialized by a reactivity profile. It starts by producing sets of representatives structures for each of the reactivity profiles using a SHAPE-directed variant of the classic Ding-Lawrence algorithm~\citep{Ding2003}. Following Deigan\etal\cite{Deigan2009}, soft constraints are used to complement the free energy contributions of the classic Turner energy model with pseudo energy contributions resulting from reactivity profiles derived from SHAPE probing experiments.  Given a reactivity $R_i$ for a position $i$, we associate a free-energy bonus to unpaired positions, defined as
$$\Delta G(i) = m \log(R_i +1 )+b$$ 
using $m=1.3$ and  $b=-0.4$.\bsi{j'avais cru comprendre que ces valeurs avaient été adapté pour IPANEMAP. Sont elles paramétrables lorsuq'ion lance IPANEMAP? Si oui il faudrait peut etre en toucher un mot qque part?} Those values are compared to those used by Deigan\etal\cite{Deigan2009}, based on the rationale that lower absolute values for pseudo-energy bonuses increase the chance of structures being simultaneously supported by multiple conditions. Those pseudo energy contributions effectively direct our predictions towards a subset of structures that are in good agreement with probing data.

@@

@@

\paragraph{Comparison and clustering of conditions.}
Faced with diverse probing conditions, we first assess the compatibility of the conclusions drawn from different probing data, including the probing-free run of \OurTool as a control. We use the methodology described in the material and methods~\ref{sec:dotplots} and, for each condition, compute the base pair probability distribution (aka \emph{dot-plot}) in the  pseudo-Boltzmann ensemble, induced by the reactivity profile. We then computed the ensemble distance, the squared Euclidean distance between dot plots, for each pair of conditions. Figure~\ref{fig:PCA} summarizes the pairwise distance, projected onto a 2D surface by a principal component analysis.

@@

\bsi{sauf erreur de ma part le cluster B des parias c'est tous les CE sans Mg .je me demande s'ils n'auraient pas tous un même biais expérimental...}

@@

	\caption{Discretized ensemble distance induced by conditions. Conditions ordered by spectral biclustering. Conditions regrouped within clusters by k-mean clustering appear as blocks on the x and y axis.}\label{fig:biclustering}
\end{figure}

### 2019-06-21 SuppMat.tex
Updates from Overleaf

 \Heatset{min=0.4,  
	max=1,   
	max colour=Aquamarine3, % colour at maximum
	min colour=BadCol,      % colour at minimum
	Min colour=BadCol, % colour for values below min
	Max colour=Aquamarine3   % colour for values above max
}
\begin{table}[H]
\centering
\newcommand{\B}{\multicolumn{1}{c}{$\bullet$}}
\newcommand{\BR}{\multicolumn{1}{c}{$\bullet$}}
\newcommand{\D}{\multicolumn{1}{c}{\color{gray}$\circ$}}
\newcommand{\DR}{\multicolumn{1}{c}{\color{gray}$\circ$}}
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{@{}lHHHHHHHHHHHHHHHH@{}}
 	\toprule
 	                              & \multicolumn{8}{l}{ \OurTool{}}                                     & \multicolumn{4}{l}{\Software{RNAfold} -- MFE mode} & \multicolumn{4}{l}{\Software{RNAfold} -- MEA mode}  \\
 	\textbf{CMCT}                 & \D    & \B    & \D       & \D    & \D    & \B       & \B    & \BR   & \D       & \D    & \B    & \DR                     & \D    & \D    & \B       & \D                       \\
 	\textbf{NMIA}                 & \D    & \D    & \B       & \D    & \B    & \D       & \B    & \BR   & \D       & \D    & \D    & \BR                     & \D    & \D    & \D       & \B                       \\
 	\textbf{DMS}                  & \D    & \D    & \D       & \B    & \B    & \B       & \D    & \BR   & \D       & \B    & \D    & \DR                     & \D    & \B    & \D       & \D                       \\ \midrule
 	5SRNA,E.Coli                  & 0.25  & 0.238 & 0.247    & 0.244 & 0.247 & 0.247    & 0.254 & 0.241 & 0.241    & 0.686 & 0.254 & 0.686                   & 0.241 & 0.686 & 0.269    & 0.686                    \\
 	glycineriboswitch,F.nucleatum & 0.568 & 0.627 & 0.868    & 0.952 & 0.868 & 0.658    & 0.868 & 0.868 & 0.306    & 0.313 & 0.395 & 0.313                   & 0.593 & 0.593 & 0.693    & 0.6                      \\
 	cidGMPriboswitch,V.Cholerae   & 0.654 & 0.77  & 0.654    & 0.77  & 0.654 & 0.77     & 0.654 & 0.77  & 0.77     & 0.77  & 0.667 & 0.77                    & 0.77  & 0.72  & 0.667    & 0.77                     \\
 	P4P6domain                    & 0.864 & 0.856 & 0.881    & 0.864 & 0.864 & 0.856    & 0.864 & 0.856 & 0.837    & 0.808 & 0.773 & 0.714                   & 0.845 & 0.808 & 0.781    & 0.722                    \\
 	adenineriboswitch,add         & 1     & 0.956 & 1        & 0.977 & 1     & 0.956    & 1     & 1     & 1        & 0.333 & 0.41  & 1                       & 1     & 0.333 & 0.356    & 0.306                    \\
 	tRNAphenylalanineyeast        & 0.286 & 0.746 & 0.976    & 0.746 & 0.976 & 0.746    & 0.976 & 0.976 & 0.976    & 0.976 & 0.976 & 0.976                   & 0.334 & 0.976 & 0.976    & 0.976                    \\ \midrule
 	Average                       & 0.604 & 0.7   & 0.77     & 0.76  & 0.77  & 0.705    & 0.77  & 0.785 & 0.69     & 0.65  & 0.58  & 0.74                    & 0.63  & 0.69  & 0.62     & 0.68                     \\ \bottomrule
 \end{tabular}
\end{adjustbox}
\caption{GM of the structures predicted with \OurTool{}, compared to predictions of \Software{RNAfold} in energy mimization (MFE) and accuracy maximization (MEA) modes.}
%( ref. $supplementary\_data/benchmark\_6RNAs$)}
\end{table}
\subsection*{Stablity analysis}
\begin{table}[H]
\centering
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{lHHHHHHHHHHHHHHHHHHHHH}\toprule
 &\multicolumn{3}{l}{ NMIA} & \multicolumn{3}{l}{ DMS} & \multicolumn{3}{l}{CMCT} &\multicolumn{3}{l}{ NMIA+DMS} & \multicolumn{3}{l}{ NMIA+CMCT} & \multicolumn{3}{l}{DMS+CMCT}& \multicolumn{3}{l}{NMIA+DMS+CMCT} \\
% & \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM }& \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM } &\multicolumn{3}{l}{ GM }\\

@@

%\section{IPANEMAP Vs Rsample}
\section*{Mono probing benchmark (Hadjin~\emph{et al}~\cite{Hajdin2013} dataset)}

{\centering
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{@{}llll@{}}
 	\toprule
 	RNA ID & Description                      \\ \midrule
 	A      & PreQ1riboswitchBsubtilis         & 	M      & SARScoronaviruspseudoknot        \\
 	B      & 5domainof16SrRNAEcoli            & 	N      & 5SrRNAEcoli                      \\
 	C      & SignalrecognitonparticleRNAhuman & 	O      & cyclicdiGMPriboswitchVcholerae   \\
 	D      & GroupIintronAzoarcussp           & 	P      & 5domainof23SrRNAEcoli            \\
 	E      & HIV15primepseudoknotdomain       & 	Q      & RNasePBsubtilis                  \\
 	F      & Telomerasepseudoknothuman        & 	R      & GroupIIntronTthermophila         \\
 	G      & SAMIriboswitchTtengcongensis     & 	S      & HepatitisCvirusIRESdomain        \\
 	H      & tRNA phe Ecoli                   & 	T      & 5domainof16SrRNAHvolcanii        \\
 	I      & P546domainbI3groupIintron        & 	U      & GroupIIintronOiheyensis          \\
 	J      & TPPriboswitchEcoli               & 	V      & tRNAaspyeast                     \\
 	K      & AdenineriboswitchVvulnificus     & 	W      & LysineriboswitchTmaritime        \\
 	L      & FluorideriboswitchPsyringae      & 	X      & MBoxriboswitchBsubtilis          \\
 	\bottomrule
 \end{tabular}
\end{adjustbox}\\}

\caption{Labels used as shorthands for the 24 RNAs in the Hadjin \emph{ et al.} dataset~\cite{Hajdin2013}.}
\label{clyu}

@@

\section*{Case-study: Lariat capping ribozyme of {\itshape Didymium iridis}}
\subsection*{Compatibility of accessibility profiles with native and predicted structures}
\begin{table}[H]
 \Heatset{min=0.2,  
	max=.5,   
	max colour=BadCol, % colour at maximum
	min colour=Aquamarine3,      % colour at minimum
	Min colour=Aquamarine3, % colour for values below min
	Max colour=BadCol   % colour for values above max
}
\begin{center}
\begin{tabular}{lHH}\toprule
 & \multicolumn{2}{c}{Distance of reactivity}\\
Condition & \multicolumn1c{to prediction}&\multicolumn1c{to native}\\
\toprule
\OneMSevILUMg & 0.234 & 0.2872\\
\OneMSevILU &	0.2784 & 0.2961\\
\NMIAMg &	0.2606 & 0.2518\\
\NMIA &	0.2961 & 0.3316\\
\OneMSevILUThreeMg &	0.4291 & 0.3936\\
\NMIAMgCE &	0.4291 & 0.3404\\
\NAIMg 	& 0.3493 & 0.305\\
\BzCNMg & 	0.3759 & 0.2429\\
\OneMSevMgCE &	0.4379 & 0.3759\\
\CMCTMg &	0.4911 & 0.4113\\
\OneMSevILUThree &	0.2961 & 0.3404\\
\DMSMg &	0.3493 & 0.3227\\
\NMIACE 	&0.2695 &0.2518 \\
\OneMSevCE &	0.3582 & 	0.3316\\
\BzCN &	0.4911 & 	0.4734\\
\NAICE &	0.4025 &0.4025\\
\bottomrule
\end{tabular}
\end {center}
\caption{Distance of the predicted structure from the considered probing data.}
\end{table}

@@

%\toprule
 \includegraphics[scale=\MyScale]{graphs/Supp_structures/native_structure}&
 \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7ILU_NMIAMg}& \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7ILUMg_1M7ILU3Mg}&
 \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7MgCE_NMIAMgCE}
 &
 \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7CE_NMIACE}
 & \includegraphics[scale=\MyScale]{graphs/Supp_structures/NaiMg_CMCTMg}\\
 \midrule
Native&\OneMSevILU&\OneMSevILUMg&\OneMSevMgCE& \1M7CE &\NAIMg\\
structure &+\NMIAMg&+\OneMSevILUThreeMg&+\NMIAMgCE&+\NMIACE &+\CMCTMg\\
\end{tabular}
\end{adjustbox}\\}

>>>>

\begin{table}[H]
\centering
\newcommand{\B}{\multicolumn{1}{c}{$\bullet$}}
\newcommand{\BR}{\multicolumn{1}{c}{$\bullet$}}
\newcommand{\D}{\multicolumn{1}{c}{\color{gray}$\circ$}}
\newcommand{\DR}{\multicolumn{1}{c}{\color{gray}$\circ$}}
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{@{}lHHHHHHHHHHHHHHHH@{}}
 	\toprule
 	                              & \multicolumn{8}{l}{ \OurTool{}}                                     & \multicolumn{4}{l}{\Software{RNAfold} -- MFE mode} & \multicolumn{4}{l}{\Software{RNAfold} -- MEA mode}  \\
 	\textbf{CMCT}                 & \D    & \B    & \D       & \D    & \D    & \B       & \B    & \BR   & \D       & \D    & \B    & \DR                     & \D    & \D    & \B       & \D                       \\
 	\textbf{NMIA}                 & \D    & \D    & \B       & \D    & \B    & \D       & \B    & \BR   & \D       & \D    & \D    & \BR                     & \D    & \D    & \D       & \B                       \\
 	\textbf{DMS}                  & \D    & \D    & \D       & \B    & \B    & \B       & \D    & \BR   & \D       & \B    & \D    & \DR                     & \D    & \B    & \D       & \D                       \\ \midrule
 	5SRNA,E.Coli                  & 0.25  & 0.238 & 0.247    & 0.244 & 0.247 & 0.247    & 0.254 & 0.241 & 0.241    & 0.686 & 0.254 & 0.686                   & 0.241 & 0.686 & 0.269    & 0.686                    \\
 	glycineriboswitch,F.nucleatum & 0.568 & 0.627 & 0.868    & 0.952 & 0.868 & 0.658    & 0.868 & 0.868 & 0.306    & 0.313 & 0.395 & 0.313                   & 0.593 & 0.593 & 0.693    & 0.6                      \\
 	cidGMPriboswitch,V.Cholerae   & 0.654 & 0.77  & 0.654    & 0.77  & 0.654 & 0.77     & 0.654 & 0.77  & 0.77     & 0.77  & 0.667 & 0.77                    & 0.77  & 0.72  & 0.667    & 0.77                     \\
 	P4P6domain                    & 0.864 & 0.856 & 0.881    & 0.864 & 0.864 & 0.856    & 0.864 & 0.856 & 0.837    & 0.808 & 0.773 & 0.714                   & 0.845 & 0.808 & 0.781    & 0.722                    \\
 	adenineriboswitch,add         & 1     & 0.956 & 1        & 0.977 & 1     & 0.956    & 1     & 1     & 1        & 0.333 & 0.41  & 1                       & 1     & 0.333 & 0.356    & 0.306                    \\
 	tRNAphenylalanineyeast        & 0.286 & 0.746 & 0.976    & 0.746 & 0.976 & 0.746    & 0.976 & 0.976 & 0.976    & 0.976 & 0.976 & 0.976                   & 0.334 & 0.976 & 0.976    & 0.976                    \\ \midrule
 	Average                       & 0.604 & 0.7   & 0.77     & 0.76  & 0.77  & 0.705    & 0.77  & 0.785 & 0.69     & 0.65  & 0.58  & 0.74                    & 0.63  & 0.69  & 0.62     & 0.68                     \\ \bottomrule
 \end{tabular}
\end{adjustbox}
\caption{GM of the structures predicted with \OurTool{}, compared to predictions of \Software{RNAfold} in energy mimization (MFE) and accuracy maximization (MEA) modes.}
%( ref. $supplementary\_data/benchmark\_6RNAs$)}
\end{table}
\subsection*{Stablity analysis}
\begin{table}[H]
\centering
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{lHHHHHHHHHHHHHHHHHHHHH}\toprule
 &\multicolumn{3}{l}{ NMIA} & \multicolumn{3}{l}{ DMS} & \multicolumn{3}{l}{CMCT} &\multicolumn{3}{l}{ NMIA+DMS} & \multicolumn{3}{l}{ NMIA+CMCT} & \multicolumn{3}{l}{DMS+CMCT}& \multicolumn{3}{l}{NMIA+DMS+CMCT} \\
% & \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM }& \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM } &\multicolumn{3}{l}{ GM }\\

@@

%\section{IPANEMAP Vs Rsample}
\section*{Mono probing benchmark (Hajdin~\emph{et al}~\cite{Hajdin2013} dataset)}

 \begin{table}[H]
{\centering
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{@{}llll@{}}
 	\toprule
 	RNA ID & Description                      \\ \midrule
 	A      & Pre-Q1 riboswitch, B. subtilis      & 	M      &SARS corona virus pseudoknot       \\
 	B      & 5’ domain of 16S rRNA, E. coli            & 	N      & 	5S rRNA, E. coli                      \\
 	C      &	Signal recogniton particle RNA human & 	O      & cyclic-di-GMP riboswitch, V. cholerae   \\
 	D      & 	Group I intron, Azoarcus sp.          & 	P      & 5’ domain of 23S rRNA, E. coli            \\
 	E      & 	HIV 15 prime pseudoknot domain       & 	Q      & RNase PB. subtilis                \\
 	F      & Telomerase pseudoknot human       & 	R      & 	Group I Intron, T. thermophila        \\
 	G      & 	SAM I riboswitch, T. tengcongensis   & 	S      & 	Hepatitis C virus IRES domain       \\
 	H      & 	tRNA(phe), E. coli                & 	T      & 	5' domain of 16S rRNA, H. volcanii      \\
 	I      & P546 domain, bI3 group I intron       & 	U      & 	Group II intron, O. iheyensis         \\
 	J      & TPP riboswitch, E. coli              & 	V      & 	tRNA(asp), yeast                    \\
 	K      &	Adenine riboswitch, V. vulnificus    & 	W      & 	Lysine riboswitch, T. maritima        \\
 	L      & Fluoride riboswitch, P. syringae     & 	X      & M-Box riboswitch, B. subtilis          \\
 	\bottomrule
 \end{tabular}
\end{adjustbox}\\}

\caption{Labels used as shorthands for the 24 RNAs in the Hajdin \emph{ et al.} dataset~\cite{Hajdin2013}.}
\label{clyu}

@@

\section*{Case-study: Lariat capping ribozyme of {\itshape Didymium iridis}}
\subsection*{Compatibility of accessibility profiles with native and predicted structures}
\begin{table}[H]
 \Heatset{min=0.2,  
	max=.5,   
	max colour=BadCol, % colour at maximum
	min colour=Aquamarine3,      % colour at minimum
	Min colour=Aquamarine3, % colour for values below min
	Max colour=BadCol   % colour for values above max
}
\begin{center}
\begin{tabular}{lHH}\toprule
 & \multicolumn{2}{c}{Distance of reactivity}\\
Condition & \multicolumn1c{to prediction}&\multicolumn1c{to native}\\
\toprule
\Bull{C}~\OneMSevILUMg & 0.234 & 0.2872\\
\Bull{A}~\OneMSevILU &	0.2784 & 0.2961\\
\Bull{A}~\NMIAMg &	0.2606 & 0.2518\\
\Bull{A}~\NMIA &	0.2961 & 0.3316\\
\Bull{C}~\OneMSevILUThreeMg &	0.4291 & 0.3936\\
\Bull{E}~\NMIAMgCE &	0.4291 & 0.3404\\
\Bull{G}~\NAIMg 	& 0.3493 & 0.305\\
\Bull{H}~\BzCNMg & 	0.3759 & 0.2429\\
\Bull{E}~\OneMSevMgCE &	0.4379 & 0.3759\\
\Bull{G}~\CMCTMg &	0.4911 & 0.4113\\
\Bull{D}~\OneMSevILUThree &	0.2961 & 0.3404\\
\Bull{F}~\DMSMg &	0.3493 & 0.3227\\
\Bull{B}~\NMIACE 	&0.2695 &0.2518 \\
\Bull{B}~\OneMSevCE &	0.3582 & 	0.3316\\
\Bull{B}~\BzCN &	0.4911 & 	0.4734\\
\Bull{B}~\NAICE &	0.4025 &0.4025\\
\bottomrule
\end{tabular}
\end {center}
\caption{Distance of the predicted structure from the considered probing data.}
\end{table}

@@

%\toprule
 \includegraphics[scale=\MyScale]{graphs/Supp_structures/native_structure}&
 \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7ILU_NMIAMg}& \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7ILUMg_1M7ILU3Mg}&
 \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7MgCE_NMIAMgCE}
 &
 \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7CE_NMIACE}
 & \includegraphics[scale=\MyScale]{graphs/Supp_structures/NaiMg_CMCTMg}\\
 \midrule
Native&\OneMSevILU&\OneMSevILUMg&\OneMSevMgCE& \OneMSevCE &\NAIMg\\
structure &+ \NMIAMg&+ \OneMSevILUThreeMg&+ \NMIAMgCE&+ \NMIACE &+ \CMCTMg\\
\end{tabular}
\end{adjustbox}\\}
